---
title: "God and Bad Plot"
author: "Margarita Alfaro"
date: "3/12/2022"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme: simplex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = '../Output/', warning = FALSE, message = FALSE)
```

### Introduction ###
This assignment is about the creation of two different version of a plot, a bad and a good plot was created based on the tidy tuesday Chocolate Bar Ratings Data from 2022-01-18.

### Load Libraries ###
```{r}
library(here)
library(tidyverse)
library(ggplot2)
library(beyonce)
library(dplyr)
```

### Load Data ###
```{r}
chocolate <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv')
```

### Bad Plot ###
#### filtering out the data 
```{r}
chocodata<-chocolate %>% # rename our new data
  select(company_location, cocoa_percent) %>% #select specific columns from the data
   filter(company_location == "U.S.A." | company_location == "France" | company_location == "U.K." | company_location == "Spain" | company_location == "Italy" | company_location == "Mexico" | company_location == "El Salvador") # filters specific country form the data set
```

#### plottling the data
```{r}
chocodata %>%
  ggplot(aes(x= company_location, y = cocoa_percent))+
  geom_jitter(color = "yellow") +
  labs(x= "Location", y = "Percent") # label the x and y-axis
```

### Comments for the bad plot ###

* ##### The numbers for the percents (%) are to many that is hard to observed the specific values for the percent.
* ##### The color yellow makes the plot difficult to read it.
* ##### The dots cannot be seen clearly.
* ##### It doesn't have a title.
* ##### The plot doesn't say what is about and even y- axis for the percent it doesn't say what is the percent about it.


### Good Plot ###
#### filtering our data
```{r}
chocodata<-chocolate %>% # rename our new data
  select(company_location, cocoa_percent) %>% #select specific columns from the data
  filter(company_location == "U.S.A." | company_location == "France" | company_location == "U.K." | company_location == "Spain" | company_location == "Italy" | company_location == "Mexico" | company_location == "El Salvador") %>% # filters specific country form the data set
  filter(cocoa_percent == "60%" | cocoa_percent == "65%" | cocoa_percent == "70%" | cocoa_percent == "75%" | cocoa_percent == "80%" | cocoa_percent == "85%" | cocoa_percent == "90%" | cocoa_percent == "95%") # filter specific cocoa percent from our data set
```

#### plottling the data
```{r}
chocodata %>%
  ggplot(aes(x = company_location, y = cocoa_percent))+
  geom_count(color = "brown") +
labs(x= "Company Location", y = "Cocoa Percent", # label the x and y-axis
     title = "Chocolate", # adds name to our title
     subtitle = "Manufacturers with different cocoa percentages according with their location",
     caption = "Source: 2022-01-18 TidyTuesday data Provided by flavor of cacao") #adds a caption from where our data was obtained
```

### Comments for the good plot ###

* ##### It has a title.
* ##### The dots can be seen clearly.
* ##### The percents were filtered and now is more easy to read.
* ##### The y-axis for the percent states that is about cocoa percent.
* ##### The plot has a source from where the data was obtained.


